\documentclass{article}

\usepackage[a4paper, total={8in, 10in}]{geometry}
\usepackage[T1]{fontenc} % Needed voor special characters
\usepackage[utf8]{inputenc} % Use correct encoding
% \usepackage{lmodern} % use this if text looks weird
\usepackage[english]{babel} % Language
\usepackage{amsmath} % Math
\usepackage{amssymb} % More Math
\usepackage{graphicx} % Images

\title{Homemade Pizza}
\author{}
\date{}

\begin{document}

\maketitle

% Write document here

\section{Ingredients (1 Pizza)}

\begin{itemize}
    \item 180ml warm water
    \item 7g instant yeast
    \item 240g all purpose flour
    \item 7g salt
    \item pinch of sugar
    \item 4 tablespoons of olive oil
\end{itemize}

\section{Instructions}

\begin{enumerate}
    \item Yeast step
        \begin{enumerate}
            \item Add the warm water to a bowl.
            \item Add the sugar to the bowl.
            \item Add the yeast to the bowl.
            \item Give it a quick stir.
            \item Let it sit for 5-7 minutes until frothing.
        \end{enumerate}
    \item Flour step
        \begin{enumerate}
            \item Add the flour to the bowl.
            \item Add the salt to the bowl.
            \item Mix the bowl.
        \end{enumerate}
    \item Slowly pour and mix the flour into the water-yeast mix. Depending on consistency you can add flour or water.
    \item In the bowl, knead the dough until you have bounce-back.
    \item Rising step
        \begin{enumerate}
            \item Add a 3 tablespoons of olive oil into a bowl.
            \item Add the ball of dough into the bowl.
            \item Cover it and place into warm space (50C\textdegree)
        \end{enumerate}
    \item Punch the dough down, place the dough on a liberally floured surface, and flour the top lightly.
    \item Roll the dough out, pick it up and stretch it out.
    \item Mold into the form of your pizza, coat with the last tablespoon olive oil, and fork holes into the bottom.
    \item Add your toppings.
    \item Place in oven at 220C\textdegree for 12 minutes.
\end{enumerate}

\end{document}
